Wheels of Misfortune: Exploring Auto Theft Trends in Ottawa

### 2024-04-22 paper/paper.qmd
updated paper

@@

# Merging 'theft_recovery' dataframe with 'auto_Data'
merged_data <- merge(auto_Data, theft_recovery, by = "theft_year", all.x = TRUE)

# Plotting the merged data as a line graph
ggplot(merged_data, aes(x = theft_year, y = recovered)) +
  geom_line() + 
  geom_point() +
  labs(x = "Year", y = "Count") +
  theme_minimal()
```
```{r}
#| label: theft-neighborhoods
#| fig-cap: "Recovery Rates from 2018 - 2023"
#| echo: false
#| warning: false
#| message: false

@@

theft_recovery <- auto_Data |>
  select(neighbourhood) |> 
  count(neighbourhood)

years_vehicle <- theft_recovery |>
  mutate(vehicle_year = as.numeric(neighbourhood))  # Convert to numeric if 'vehicle_year' is factor

# Create a scatter plot
ggplot(years_vehicle, aes(x = neighbourhood, y = n, fill = neighbourhood)) +
  geom_point() +  
  theme_minimal() + 
  theme(legend.position = "bottom") + 
  labs(x = "Vehicle Brand", y = "Count", fill = "Count", title = "Top 10 Brands with Most Auto Thefts in 2022")

>>>>

theft_count <- auto_Data |>
  select(theft_year)

theft_count |>
  ggplot(mapping = aes(x = theft_year)) +
  geom_bar() +
  labs(x = "Age group", y = "Number of observations") +
  theme(legend.position = "bottom")

@@

@@
